---
title: "Effects of Two Herbicide Treatments on Plant Growth"
author: "EDeomano"
date: "10 May 2018"
output:
  html_document:
    toc: true
    number_sections: true
editor_options: 
  chunk_output_type: console
---

# Setup
```{r loadPackages, message=FALSE}
library(tidyverse)
library(pander)
```

# Data Description
Data collected from a design experiment with two herbicides.  Parameters on plan growth were measured.

The data has a total of `r nrow(PlantGrowth)` data points.  While the treatment classifications are `r pander(levels(PlantGrowth$group))`.

```{r dataSummary}
PlantGrowth %>% 
  group_by(group) %>% 
  summarise(`Mean weight` = mean(weight),
            n = n()) %>%
  rename(Treatment = group) %>% 
  pander(justify = "lrr",
         caption = "*Sample sizes and mean*")
```


```{r boxPlot, fig.width = 6, fig.height = 6, fig.cap = "*Boxplot of dried weight*"}
ggplot(PlantGrowth,
       aes(x = group, y = weight, fill = group)) +
  geom_boxplot() +
  labs(x = "Treatment",
       y = "Weight") +
  guides(fill = FALSE) +
  theme_bw()
```


# Analysis
We fit a regression model using weight as the response and group as predictor.
The model is
$$y_{ij} = \mu + \alpha_i + \varepsilon{ij}$$
```{r}
model_fit <- lm(weight ~ group, data = PlantGrowth)
anova(model_fit) %>% pander()
summary(model_fit) %>% pander()
```


# Diagnostic Plots
```{r, fig.cap = "Residuals versus Fitted Values", fig.width = 6}
plot(model_fit, which = 1)
```

```{r, fig.cap = "Normal Q-Q plot", fig.width = 6}
plot(model_fit, which = 2)
```


# Conclusion
The end!

```{r}
sessionInfo()
```

